Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-24 ECCV/paper.tex
Added results.

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers \
\pagestyle{headings}
\mainmatter
\def\ECCV12SubNumber{***}  % Insert your submission number here

@@

\titlerunning{ECCV-12 submission ID \ECCV12SubNumber}

\authorrunning{ECCV-12 submission ID \ECCV12SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV12SubNumber}

@@

\begin{abstract}
Fiducial markers are commonly used to track an object in an unknown environment
and finds use in various applications in Virtual Reality, Medical imaging,
Surveys, etc. The performance of popular fiducials is satisfactory when there is
little motion or no motion in the device obtaining the imagery. But when there
is continuous and swift motion, as in the case of low cost quadcopters,
performance of these fiducials degrade significantly due to motion blur.
Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. Our
algorithm is based on the fact that there is no blur in the direction
perpendicular to the direction of the motion.

\end{abstract}

@@

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave\cite{GaborFilter}. It is used to find high gradient
patches from the image. In our case, it will detect blur invariant sections of the fiducials We
have applied Gabor filter for eight different orientations and then calculated
L2 norm of all outputs.

@@

\textbf{Classification}: Each synthetic fiducial pattern is blurred along 36
orientations (0, 10, 20, \ldots , 350) and intensity profile along first
principal component from every output is taken as training data for that fiducial pattern.
Training data for patterns having same number of rings is grouped together;
e.g., in two bit binary coded fiducial, training data for pattern “01” and “10”
will be grouped together. Now, depending on the number of detected rings, test
pattern is matched against corresponding training data using K-Nearest Neighbor
Classifier (K=5).

\section{Experimental Validation}
\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker.
\subsubsection{Comparison with ARTag}
\subsubsection{Comparison with Blut}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers \
\pagestyle{headings}
\mainmatter
\def\ECCV14SubNumber{150}  % Insert your submission number here

@@

\titlerunning{ECCV-14 submission ID \ECCV14SubNumber}

\authorrunning{ECCV-14 submission ID \ECCV14SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV14SubNumber}

@@

\begin{abstract}
Fiducial markers are commonly used to track an object in an unknown environment
and finds use in various applications in Virtual Reality, Medical imaging,
Surveys, etc. The performance of popular fiducials is satisfactory when there is
little motion or no motion in the device obtaining the imagery. But when there
is continuous and swift motion, as in the case of low cost quadcopters,
performance of these fiducials degrade significantly due to motion blur.
Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. Our
algorithm is based on the fact that there is no blur in the direction
perpendicular to the direction of the motion.
\dots
\keywords{Fiducials, Blur Invariant Tracking,}
\end{abstract}

@@

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations and then calculated
L2 norm of all outputs.

@@

\textbf{Classification}: Each synthetic fiducial pattern is blurred along 36
orientations (0, 10, 20, \ldots , 350) and intensity profile along first
principal component from every output is taken as training data for that fiducial pattern.
Training data for patterns having same number of rings is grouped together;
e.g., in two bit binary coded fiducial, training data for pattern ``01'' and
``10'' will be grouped together. Now, depending on the number of detected
rings, test pattern is matched against corresponding training data using
K-Nearest Neighbor Classifier (K=5).

\begin{figure}
\centering
  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_180.jpg}  
  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_45.jpg}
  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_90.jpg}  
  \caption{Sample images used to create training data for the fiducial pattern
  with binary code ``01''}
\end{figure}

\section{Experimental Validation}
Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.

\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_00.jpg}
  \caption{Sample output for the fiducial pattern with binary code ``00''}
  \label{fig:output0}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_01.jpg}
  \caption{Sample output for the fiducial pattern with binary code ``01''}
  \label{fig:output1}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_10.jpg}
  \caption{Sample output for the fiducial pattern with binary code ``10''}
  \label{fig:output2}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_11.jpg}
  \caption{Sample output for the fiducial pattern with binary code ``11''}
  \label{fig:output3}
\end{figure}

Our system has also been tested on images containing multiple fiducial patterns
in the same frame. Our algorithm successfully detected all fiducial patterns as
well as correctly classified them as shown in Fig. \ref{fig:output_all}
\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_all_2.jpg}
  \caption{Sample output containing all two bit binary coded fiducial patterns}
  \label{fig:output_all}
\end{figure}

\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker.
\subsubsection{Comparison with ARTag}
\subsubsection{Comparison with Blut}
